%====================
% EXPERIENCE A
%====================
\subsection{{Aktech Labs, Cirun.io\hfill May 2022 --- Present}}
\subtext{Part-Time Freelance Software Test Engineer \hfill Remote}
\begin{zitemize}
\item Automated testing of the CI/CD service named Cirun.io
using Cypress, Javascript and GitHub Actions.
\end{zitemize}


%====================
% EXPERIENCE A
%====================
\subsection{{Gartner\hfill Jun 2021 --- Apr 2022}}
\subtext{Software Test Engineer \hfill Remote}
\begin{zitemize}
\item Automated the internal portal using UIPath.
\item Automated test script to test the application using Nightwatch
\item Manual and Automated testing of all the services used in the application.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Cognizant\hfill Dec 2017 --- Jun 2021}}
\subtext{Programmer Analyst, Travelers - Insurance \hfill Chennai, TN}
\begin{zitemize}
\item Involved in Automation Testing - Automated script creation and maintenance (script error
debugging) \& Automated script enhancements.
\item Create and maintain all the release and project specific user stories and tasks using Rally.
\item Identify release and project specific milestones, external milestones,
dependencies, issues, risks and assumptions.
\end{zitemize}


\subtext{Programmer Analyst Trainee, Met Life \hfill Chennai, TN}
\begin{zitemize}
\item Involved in maintaining and enhancing CAS Application.
\item Developed selenium codes in RAD Application.
\item Fixed various security flaws by analyzing the requirement, identified the desired scenarios,
made relevant code changes, and performed Unit and Manual Testing on local as well as
the application.
\item Verified logs for all the applications and tracked the exceptions.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
% \subsection{{ROLE / PROJECT C \hfill MMM YYYY --- MMM YYYY}}
% \subtext{company C \hfill somewhere, state}
% \begin{zitemize}
% \item Donec volutpat turpis et placerat pharetra.
% \item Sed sit amet sem facilisis, scelerisque lectus aliquam, accumsan purus.
% \item Aliquam at urna congue dolor luctus sodales.
% \item Quisque vitae tortor at elit tincidunt molestie sed ac quam.
% \end{zitemize}

% %====================
% % EXPERIENCE D
% %====================
% \subsection{{ROLE / PROJECT D \hfill MMM YYYY --- MMM YYYY}}
% \subtext{company D \hfill somewhere, state}
% \begin{zitemize}
% \item Vestibulum accumsan massa quis dignissim faucibus.
% \item Maecenas suscipit mi ut ullamcorper pharetra.
% \item In vitae ligula tristique, iaculis tortor in, egestas magna.
% \item In fringilla purus malesuada lectus imperdiet pulvinar.
% \item Nulla eu dolor congue, mollis dui a, eleifend purus.
% \end{zitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
